Extracting production locations for each species to obtain environmental forcings

### 2025-07-08 02_extracting_production_locations.qmd
Updating FAO data

Isolate production data for Atlantic salmon.
```{r rich-raw-processing}
#| eval: false

>>>>

Isolate production data for Atlantic salmon.

```{r clean-raw-data}
quantity <- file.path(rawdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
  read.csv() %>% 
  clean_names() %>% 
  mutate(value = set_units(value, "t")) %>% 
  select(-measure)

environment_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
  read.csv() %>% 
  distinct(Code, Name_En)

quantity <- quantity %>% 
  merge(environment_codes, by.x = "environment_alpha_2_code", by.y = "Code") %>%
  rename(environment = Name_En) %>% 
  filter(environment == "Marine") %>% 
  select(-environment_alpha_2_code)

species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
  read.csv() %>% 
  filter(str_detect(Scientific_Name, "Salmo")) %>% 
  filter(Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae")) %>% 
  distinct(X3A_Code, Scientific_Name)

quantity <- quantity %>% 
  merge(species_codes, by.x = "species_alpha_3_code", by.y = "X3A_Code") %>% 
  filter(!is.na(Scientific_Name)) %>% 
  select(-species_alpha_3_code)

status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
  read.csv() %>% 
  distinct(Symbol, Name_En, Description_En)

quantity <- quantity %>% 
  merge(status_codes, by.x = "status", by.y = "Symbol") %>% 
  rename(status_nm = Name_En,
         status_description = Description_En) %>% 
  select(-status)

```{r rich-raw-processing}
#| eval: false
